Characterisation of MSC in clinical trial reports: analysis of published descriptors

### 2020-04-19 paper2_figures_viridis_checked.Rmd
fig 8 added

# Figures

@@

```{r}
fig7 <- charact_by_marker_summary %>% 
  ggplot() +
  geom_bar(aes(x = marker2, y = n, fill = test_status),
           stat = "identity", width = 0.6) +
  scale_fill_manual(values =  pal[c(1, 2, 5)],
                    name = "Test results",
                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 90, 10),
                     minor_breaks = seq(0, 90, 10),
                     limits = c(0, 90),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = "Characterisation attribute") +
  geom_rect(xmin = 1.5, xmax = 11.5,
            ymin = -Inf, ymax = Inf,
            size = 1, linetype = 1, 
            colour = "black", alpha = 0) +
  labs(title = "Wilson, Alison, Figure 7. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 6, colour = "black",
                                   angle = -60, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in"))

@@

```{r}
#alt fig
fig7alt <- charact_by_marker_ref %>% 
  ggplot() +
  geom_tile(aes(x = factor(`Ref #`), y = marker2 , fill = test_status),
            colour = "white")+
    scale_fill_manual(values =  pal[c(1, 2, 5)],
                    name = "Test results",
                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
  scale_x_discrete(name = "Reference",
                     expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0, 0), name = "Characterisation attribute") +
  geom_rect(ymin = 1.5, ymax = 11.5,
            xmin = -Inf, xmax = Inf,
            size = 1, linetype = 1,
            colour = pal[6], alpha = 0) +
  labs(title = "Wilson, Alison, Figure 7ALT. TOP" ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 5, colour = "black", 
                                   angle = 90, hjust = 0, vjust = 0.3),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in"))

ggsave("figs/fig_7_alt.tif", 
       plot = fig7alt, 
       device = device,
       width = fig_w_2, 
       height = fig_w,
       units = units,
       dpi = dpi)

@@

# Figure 8

>>>>

```{r}
dat %>% group_by(other_functionality) %>% 
  summarise(n = length(other_functionality), pc = n/84)
```
# Figures

@@

```{r}
fig7 <- charact_by_marker_summary %>% 
  ggplot() +
  geom_bar(aes(x = marker2, y = n, fill = test_status),
           stat = "identity", width = 0.6) +
  scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
                    name = "Test results",
                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 90, 10),
                     minor_breaks = seq(0, 90, 10),
                     limits = c(0, 90),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = "Characterisation attribute") +
  geom_rect(xmin = 1.5, xmax = 11.5,
            ymin = -Inf, ymax = Inf,
            size = 1, linetype = 1, 
            colour = "black", alpha = 0) +
  labs(title = "Wilson, Alison, Figure 7. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 6, colour = "black",
                                   angle = -60, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in"))

@@

# Possible alternative to Fig 7 (and 6b)
```{r}
#alt fig
fig7alt <- charact_by_marker_ref %>% 
  ggplot() +
  geom_tile(aes(x = factor(`Ref #`), y = marker2 , fill = test_status),
            colour = "white")+
    scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
                    name = "Test results",
                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
  scale_x_discrete(name = "Reference",
                     expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0, 0), name = "Characterisation attribute") +
  geom_rect(ymin = 1.5, ymax = 11.5,
            xmin = -Inf, xmax = Inf,
            size = 1, linetype = 1,
            colour = "black", alpha = 0) +
  labs(title = "Wilson, Alison, Figure 7ALT. TOP" ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 5, colour = "black", 
                                   angle = 90, hjust = 0, vjust = 0.3),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in"))

ggsave("figs/fig_7_charact_by_marker_ALTERNATIVE.tif", 
       plot = fig7alt, 
       device = device,
       width = fig_w_2, 
       height = fig_w,
       units = units,
       dpi = dpi)

@@

# Figure 8
```{r}
functionality <- dat %>% 
  select(O, A, C, other_functionality) %>% 
  pivot_longer(cols = everything(), names_to = "Functionality", values_to = "status") %>% 
  group_by(Functionality, status) %>% 
  summarise(n = length(status))

# status
# recode status
functionality <- functionality %>%
  mutate(status = recode_factor(status,
                                p = "Performed",
                                m = "Mentioned",
                                n = "Not mentioned"))

functionality$status <- fct_relevel(functionality$status,
                                    "Not mentioned",
                                    "Mentioned",
                                    "Performed")

# recode functionality
functionality <- functionality %>%
  mutate(potency_ass = recode_factor(Functionality,
                                     other_functionality = "Other functionality",
                                     C = "Chondrogenesis",
                                     A = "Adipogenesis",
                                     O = "Osteogenesis"))

functionality$potency_ass <- fct_relevel(functionality$potency_ass,
                                         "Other functionality",
                                         "Chondrogenesis",
                                         "Adipogenesis",
                                         "Osteogenesis")

```{r}
fig8 <- functionality %>% 
  ggplot() +
  geom_bar(aes(x = potency_ass, y = n, fill = status),
           stat = "identity", position = position_dodge()) +
  scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
                    name = "Assessment",
                    guide = guide_legend(nrow = 2, title.position = "top", title.hjust = 0.5 )) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 80, 10),
                     minor_breaks = seq(0, 80, 10),
                     limits = c(0, 80),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = "Functionality") +
  labs(title = "Wilson, Alison, Figure 8. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in")) +
  coord_flip()

ggsave("figs/fig_8_functionality_assessment.tif", 
       plot = fig8, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)
```
